Model LF

### 2022-10-29 Final test.Rmd
Commit

COMMENT> 
IDENTITY> ur
EQ> ur = ur_ds -(alpha_140 + alpha_141*SD1 + alpha_142*SD2 + alpha_143*SD3) - mean_ur

@@

nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
```

>>>>

COMMENT> 
IDENTITY> ur
EQ> ur = ur_ds +alpha_140 + alpha_141*SD1 + alpha_142*SD2 + alpha_143*SD3 - mean_ur

@@

nl_g_bs7b = Shock_bs7b$simulation$nl_g
unemp_bs7b = Shock_bs7b$simulation$unemp
yd_hk_ds_bs7b = Shock_bs7b$simulation$yd_hk_ds
wage_gap1_bs7b = Shock_bs7b$simulation$wage_gap1
wage_gap_bs7b = Shock_bs7b$simulation$wage_gap
prod_bs7b = Shock_bs7b$simulation$prod
ur_test_bs7b = Shock_bs7b$simulation$ur_test
ur_bs7b = Shock_bs7b$simulation$ur
```

## Hvorfor forskel?

```{r}
plot(ur_test_bs7b, col= "red"); lines(ur_bs7b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```
